Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-23 Docs/TODAES/paper.tex
review experimental evaluation
Signed-off-by: Mauro de Freitas <maurokenny@gmail.com>

\usepackage{hyphenat}
\hyphenation{par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.

In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks. When ILP produces a result, it provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z. On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.

Note further that all multi-core ESBMC implementations produce better results than the sequential one. In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z. However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools. When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

@@

Note that RC$6$ produced timeout for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution. No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.

>>>>

\usepackage{hyphenat}
\hyphenation{ESBMC par-ti-cu-lar func-tion ef-fect-ive consi-de-red demons-trate se-cond veri-fication covera-ge des-cribe reali-zation opera-tor re-pre-sentation methodo-lo-gy di-gi-tal chara-cteristics granu-lar ge-nerally diago-nal para-meters spe-cification re-presentable me-thods ope-rations sche-dule deve-loped des-cribes diffe-rent mo-dels sa-ving ve-rified proper-ties mini-mum mathe-matical tole-rated limi-ted op-tical net-works semi-conduc-tor go-to-pro-grams }

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}SS, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks; ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns three TOs (timeouts) related to RC6, Fuzzy and Mars benchmarks.

In contrast to ESBMC-$\nu$Z, ILP solves $5$ out of $7$ benchmarks. When ILP produces a result, it provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by ESBMC-$\nu$Z. On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.

Note further that all multi-core ESBMC implementations produce better results than the sequential one. In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $2$.$5$ times slower than ESBMC-$\nu$Z. However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools. When analyzing all benchmarks, ESBMC-PB produces TO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

@@

Note that RC$6$ produced timeouts for all implementations of ESBMC; GA did not produce the correct answer, and ILP solves correctly most benchmarks, except for Mars and Fuzzy, which produced timeouts and memory-outs in all tools that aim to find the exact solution. No tool was capable to solve Mars in less than $3600$ seconds, while GA solved all benchmarks, but mostly incorrectly.
